---
title: "Public Thought on the Black Lives Matter Movement"

subtitle: 'Investigating organizational reference in SLC & Provo, UT through talk radio and tweets'

date: "10 December 2020 | PS811 | UW-Madison"
author: "Jess Esplin"


output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

setwd("C:/Users/jesse/OneDrive - UW-Madison/2020 Fall Semester/811 Intro to R/ps811-exercises/final project")
```


## Background & Research Question

- Observations of references to local community orgs vs national/global org


- Does organizational reference vary with support for Black Lives Matter movement?


- Schattschneider (1960), Zaller (1992), Nelson & Kinder (1994)


\newpage
## Hypotheses 

- Independent variable: individual's support for (or opposition to) the Black Lives Matter movement


- Dependent variable: the organization centered/referenced in individual's expression of public thought
  - local vs national/global


- Hypothesis: Support/opposition is correlated with organization centered in discourse

  - $H_A$: $\beta \neq 0$
  
- Null: no correlation

  - $H_0$: $\beta = 0$


\newpage
## Data

- Talk radio data
  
  - SLC:
    - RadioWest @ KUER
    - The JayMac Show @ KSL Radio (formerly)
  
  - Provo: 
    - The Lisa Show @ BYU Radio
    - Top of Mind with Julie Rose @ BYU Radio

- Tweets collected by MIT Media Lab


\newpage
## Method

- Primarily inductive qualitative analysis + listening
  - Talk radio shows

- Descriptive stats + hypothesis test using t-test
  - Tweets


\newpage
## Preliminary Results
```{r, results=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
## TWEETS WORD CLOUD

# load packages
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")

# load text file with first 50 tweets
text <- readLines("1000-tweets.txt")

# convert data to corpus
tweetstext <- Corpus(VectorSource(text))

## clean up data

# convert all text to lower case
tweetstext <- tm_map(tweetstext, content_transformer(tolower))

# remove numbers
tweetstext <- tm_map(tweetstext, removeNumbers)

# remove english common stopwords
tweetstext <- tm_map(tweetstext, removeWords, stopwords("english"))

# remove custom stopwords
tweetstext <- tm_map(tweetstext, removeWords, c("like", "amp", "blacklivesmatter")) 

# remove punctuation
tweetstext <- tm_map(tweetstext, removePunctuation)

# eliminate extra white spaces
tweetstext <- tm_map(tweetstext, stripWhitespace)

# build term-document matrix
dtm <- TermDocumentMatrix(tweetstext)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)

# generate word cloud
set.seed(1234)
tweetwc <- wordcloud(words = d$word, scale=c(5,0.6),freq = d$freq, min.freq = 1,
                     max.words=200, random.order=FALSE, rot.per=0.35, 
                     colors=brewer.pal(5, "Spectral"))

print(tweetwc)

# thanks & credit on much of this code to STHDA website tutorial on word clouds: http://www.sthda.com/english/wiki/text-mining-and-word-cloud-fundamentals-in-r-5-simple-steps-you-should-know
```


\newpage
## Preliminary Results
```{r, results=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
# plot word frequencies
barplot(d[1:10,]$freq, las = 2, names.arg = d[1:10,]$word,
        col ="lightblue", main ="Most frequent words",
        ylab = "Word frequencies")
```


\newpage
## Preliminary Results: excluding "Black Lives Matter" & "BLM"
```{r, results=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
## TWEETS WORD CLOUD 2
# attempt word cloud 4 excluding black lives matter or blm words

# exclude movement names
tweetstext2 <- tm_map(tweetstext, removeWords, c("black", "lives", "matter", "blm", "blacklivesmatter")) 

# building term-document matrix
dtm <- TermDocumentMatrix(tweetstext2)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

# look at most frequent words
head(d, 10)

# create word cloud
set.seed(1234)
tweetwc2 <- wordcloud(words = d$word, freq = d$freq, min.freq = 1,
                     max.words=200, random.order=FALSE, rot.per=0.35, 
                     colors=brewer.pal(5, "Dark2"))

print(tweetwc2)
```


\newpage
## Preliminary Results: excluding "Black Lives Matter" & "BLM"
```{r, results=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
# plot word frequencies
barplot(d[1:10,]$freq, las = 2, names.arg = d[1:10,]$word,
        col ="lightblue", main ="Most frequent words",
        ylab = "Word frequencies")
```


\newpage
## Discussion & Conclusion

- xxx
  - xxx

- xxx

- xxx
  - xxx
  - xxx
  - xxx


\newpage
## References

\begin{itemize}
\item[1)] xxx
\item[2)] xxx
\item[3)] xxx
\item[4)] xxx
\item[5)] xxx
\item[6)] xxx
\item[7)] xxx
\end{itemize}